Create Label Density

### 2022-02-16 eda/calculate_label_density.Rmd
clean up HM labeled amicus file

```{r}
labeled_amicus <- labeled_amicus %>% 
  mutate(manual_divide = ifelse(!is.na(divided_1) | !is.na(divided_2), 1, 0))

# d1
d1_am <- labeled_amicus %>% filter(!is.na(divided_1)) %>% 
  select(case:fem, -text, divided_1,d1_label_code) %>% 
  rename(text = divided_1,label = d1_label_code)
```

```{r}
labeled_amicus %>% 
  filter(!is.na(divided_2) & !is.na(divided_1))
```

>>>>

```{r}
# rmv texts w/o labels & indicate which texts were manually split
labeled_amicus <- labeled_amicus %>% 
  mutate(manual_divide = ifelse(!is.na(divided_1) | !is.na(divided_2), 1, 0)) %>% 
  filter(hm_label_code_s != "no labels") %>% 
  mutate(divided_1 = ifelse(id == 861816856607, text, divided_1))

top <- labeled_amicus %>% 
  filter(excerpt_divided_if_yes_top_or_bottom_coded %in% c("top", "all(short)")) %>% 
  select(case:fem, -text, text = divided_1, hm_label_code_s)

bottom <- labeled_amicus %>% 
  filter(excerpt_divided_if_yes_top_or_bottom_coded == "bottom") %>% 
  select(case:fem, -text, text = divided_2, hm_label_code_s)

not_div <- labeled_amicus %>% 
  filter(excerpt_divided_if_yes_top_or_bottom_coded == "not divided") %>% 
  select(case:fem, hm_label_code_s)

labeled_amicus_final <- rbind(top, bottom, not_div)
```

We now have a dataframe with only the following columns, with one row per labeled text.

```{r}
labeled_amicus_final %>% colnames()
```

Write to Box

```{r}
#box_write(labeled_amicus_final, dir_id = "154895322313", "labeled_amicus.csv")
```
